Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Tone down sugar references in section 2.1.

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}, yet our prior Sugar Learning Platform
made no use of this fact. By contrast, Nell augments Sugar's
affordances for \textit{action}, \textit{reflection}, and
\textit{communication} with new affordances for \textit{engagement} organized
as a modular \textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}.
In this interface, all system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with one of the
system protagonists.

>>>>

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}. Nell takes advantage of this fact 
to augment prior affordances for \textit{action}, \textit{reflection}, and
\textit{communication} with new affordances for \textit{engagement} in the form of
a modular \textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}.
In this interface, all system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with one of the
system protagonists.
